---
output:
  word_document: default
  html_document: default
  pdf_document: default
---

\#preparation des données

```{r warning=TRUE}

# src_tbls(slyr)
# 
# library(tidyverse)


library(tidyverse)
college <- read.csv('http://672258.youcanlearnit.net/college.csv')
college <- college %>%
  mutate(state=as.factor(state), region=as.factor(region),
         highest_degree=as.factor(highest_degree),
         control=as.factor(control), gender=as.factor(gender),
         loan_default_rate=as.numeric(loan_default_rate))




```

# How many schools are in each region?

# This calls for a bar graph!

```{r}

ggplot(data=college) +
  geom_bar(mapping=aes(x=region))

```

# Break it out by public vs. private

```{r}

ggplot(data=college) +
  geom_bar(mapping=aes(x=region, color=control))
```

# Well, that's unsatisfying! Try fill instead of color

```{r}
ggplot(data=college) +
  geom_bar(mapping=aes(x=region, fill=control))
```

# How about average tuition by region?

# First, I'll use some dplyr to create the right tibble

```{r}

college %>%
  group_by(region) %>%
  summarize(average_tuition=mean(tuition))

```

# And I can pipe that straight into ggplot

```{r}


data_college <- college %>%
  group_by(region) %>%
  summarize(average_tuition=mean(tuition))

# data_college %>%  ggplot() +
#   geom_bar(mapping=aes(x=region, y=average_tuition))

```

# But I need to use a column graph instead of a bar graph to specify my own y

```{r}

college %>%
  group_by(region) %>%
  summarize(average_tuition=mean(tuition)) %>%
  ggplot() +
  geom_col(mapping=aes(x=region, y=average_tuition))


```
